---
title: "final_project"
author: "Shai-Li Ron"
date: "4/3/2021"
output: html_document
---

---
title: "final_data"
author: "Shai-Li Ron"
date: "3/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(dplyr)
library(janitor)
library(primer.data)
library(rstanarm)


```

```{r}
# Moving the data from the cvs
covid_vac <- read_csv(file = "raw_data/vaccinated_city_table_ver_0022.csv", col_types = cols(
  .default = col_character(),
  CityCode = col_double(),
  Date = col_date(format = "")
)) 

```



```{r}
x <- covid_vac %>% 
clean_names 

# filter((first_dose_0_19 == "<15"),(first_dose_20_29 == "<15"), (first_dose_30_39 == "<15"), (first_dose_40_49 == "<15"), (first_dose_40_49 == "<15"), (first_dose_40_49 == "<15"), (first_dose_40_49 == "<15"), (first_dose_40_49 == "<15")



#mutate(first_dose_0_19 == "<15", 15)

#city name
#total first vaccine and total second vaccine

```

```{r}
clean_15 <- covid_vac %>% 
  clean_names() %>% 
  mutate(first_dose_0_19 = ifelse(first_dose_0_19 =="<15", 0, first_dose_0_19)) %>% 
  mutate(first_dose_20_29 = ifelse(first_dose_20_29 =="<15", 0, first_dose_20_29)) %>% 
  mutate(first_dose_30_39 = ifelse(first_dose_30_39 =="<15", 0, first_dose_30_39)) %>% 
  mutate(first_dose_40_49 = ifelse(first_dose_40_49 =="<15", 0, first_dose_40_49)) %>% 
   mutate(first_dose_50_59 = ifelse(first_dose_50_59 =="<15", 0, first_dose_50_59)) %>% 
 mutate( first_dose_60_69 = ifelse(first_dose_60_69 =="<15", 0,  first_dose_60_69)) %>% 
  mutate(first_dose_70_79 = ifelse(first_dose_70_79 =="<15", 0, first_dose_70_79)) %>% 
  mutate(first_dose_80_89 = ifelse(first_dose_80_89 =="<15", 0, first_dose_80_89)) %>% 
  mutate(first_dose_90 = ifelse(first_dose_90 =="<15", 0, first_dose_90))%>% 
    mutate(second_dose_0_19 = ifelse(second_dose_0_19 =="<15", 0, first_dose_0_19)) %>% 
  mutate(second_dose_20_29 = ifelse(second_dose_20_29 =="<15", 0, second_dose_20_29)) %>% 
  mutate(second_dose_30_39 = ifelse(second_dose_30_39 =="<15", 0, second_dose_30_39)) %>% 
  mutate(second_dose_40_49 = ifelse(second_dose_40_49 =="<15", 0, second_dose_40_49)) %>% 
   mutate(second_dose_50_59 = ifelse(second_dose_50_59 =="<15", 0, second_dose_50_59)) %>% 
 mutate(second_dose_60_69 = ifelse(second_dose_60_69 =="<15", 0,  second_dose_60_69)) %>% 
  mutate(second_dose_70_79 = ifelse(second_dose_70_79 =="<15", 0, second_dose_70_79)) %>% 
  mutate(second_dose_80_89 = ifelse(second_dose_80_89 =="<15", 0, second_dose_80_89)) %>% 
  mutate(second_dose_90 = ifelse(second_dose_90 =="<15", 0, second_dose_90)) %>% 
   select(city_code, city_name, date, starts_with("first_dose"), starts_with("second_dose")) 
  

 # select(city_code, city_name, date, starts_with("first_dose")) 
  # mutate(total = sum(first_dose_90))

# still trying to figure out how to do a total of them by each date, seems a little complicated. 

```

```{r}
clean_15
```

Socio-economic impact on vaccination rate?
By city code
population of each city


Final Project Milestone #6 due Friday. You must have a working Shiny App. It can be a mess, but it must have at least one attractive graphic with your data. You must have a Model panel with a fitted model and description thereof. You must have an About panel. Submit the url for your Shiny App via Canvas.


```{r}
as_num <- clean_15 %>% 
  mutate_at(vars(-c("city_name", "date")), as.numeric) 

  
# mutate(first_dose_0_19 = as.numeric(first_dose_0_19)) %>% 
#   mutate(first_dose_20_29 = as.numeric(first_dose_20_29)) %>% 
#   mutate(first_dose_30_39 = as.numeric(first_dose_30_39)) %>% 
#   mutate(first_dose_40_49 = as.numeric(first_dose_40_49)) %>% 
#   mutate(first_dose_50_59 = as.numeric(first_dose_50_59)) %>% 
#   mutate(first_dose_60_69 = as.numeric(first_dose_60_69)) %>% 
#   mutate(first_dose_70_79 = as.numeric(first_dose_70_79)) %>% 
#   mutate(first_dose_80_89 = as.numeric(first_dose_80_89)) %>% 
#   mutate(first_dose_90 = as.numeric(first_dose_90)) 

```


```{r}
as_num %>% 
    filter(city_code == c(5000, 3000, 472, 3797)) %>% 
  select(city_code, date, starts_with("first_dose")) %>% 
  group_by(city_code, date) %>% 
  mutate(total = sum(first_dose_0_19, first_dose_20_29, first_dose_30_39, first_dose_40_49, first_dose_50_59, first_dose_60_69, first_dose_70_79, first_dose_80_89, first_dose_90)) %>% 
  select(city_code, date, total) %>% 
  ggplot(aes(x = date,
         y = total,
         color = city_code)) +
  geom_point()

```



```{r}
 as_num %>% 
  select(city_code, date, starts_with("first_dose")) %>% 
  group_by(city_code, date) %>% 
  mutate(total = sum(first_dose_0_19, first_dose_20_29, first_dose_30_39, first_dose_40_49, first_dose_50_59, first_dose_60_69, first_dose_70_79, first_dose_80_89, first_dose_90)) %>% 
  select(city_code, date, total) %>% 
  ggplot(aes(x = date,
         y = total)) +
  geom_point()

```


```{r}

fit_obj <- stan_glm(data = as_num, 
                    formula = first_dose_50_59 ~ 1, 
                    family = gaussian, 
                    refresh = 0,
                    seed = 9)
```

```{r}
posterior_plot <- fit_obj %>% 
  as_tibble() %>% 
   rename(mu = `(Intercept)`) %>% 
  ggplot(aes(x = mu)) +
    geom_histogram(aes(y = after_stat(count/sum(count))), 
                   bins = 100) +
    labs(title = "Posterior for Number of vaccinated 50-60 year olds in any city in Israel",
         subtitle = "Most cities have about 12000 vaccinated",
         x = "Number of first-dose vaccinated 50 year olds in any given city",
         y = "Probability",
         caption = "Data source: Israeli National Health Service") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme_classic() 

 ggsave("posterior_plot.png", posterior_plot)
 
 
 posterior_plot
```


```{r}
test_plot <- as_num %>% 
  ggplot(aes(x = date,
             y = first_dose_0_19,
             color = city_code)) +
  geom_point() +
  labs(x = "Date",
       y = "Number of 0-19 Year-Olds First-Dose Vaccinated",
     title =  "Total Number of 0-19 Year-Olds Vaccinated Over Time",
       subtitle = "As time went by more 0-19 year olds got vaccinated",
       caption = "Source: Israeli National Health Service") +
  theme_gray()

  
  
  ggsave("test_plot.png", test_plot)
  

```


```{r}
total_ages <- as_num %>% 
  mutate("0-19" = sum(first_dose_0_19)) %>% 
  mutate("20-29" = sum(first_dose_20_29)) %>% 
  mutate("30-39" = sum(first_dose_30_39)) %>% 
  mutate("40-49" = sum(first_dose_40_49)) %>% 
  mutate("50-59" = sum(first_dose_50_59)) %>% 
  mutate("60-69" = sum(first_dose_60_69)) %>% 
  mutate("70-79" = sum(first_dose_70_79)) %>% 
  mutate("80-89" = sum(first_dose_80_89)) %>% 
  mutate("90" = sum(first_dose_90)) %>% 
  pivot_longer(cols = "0-19" : "90",
               names_to = "age",
               values_to = "total") %>% 
  select(age, total)  

```


```{r}
p_total_ages <- total_ages %>% 
  mutate(total = total/1000000) %>% 
  ggplot(aes(x = age, 
             y = total)) +
  geom_point() +
  labs(x = "Age Group",
       y = "Total Vaccinated First Dose (millions)",
       title =  "Total Number of Vaccinated in Each Age Group",
       subtitle = "Ages 60-69 have the most vaccinated",
       caption = "Source: Israeli National Health Service") +
  theme_bw() 
ggsave("total_ages.png", p_total_ages)
 
```

```{r}
total_ages
```


```{r}
total_ages %>% 
   ggplot(aes(x = age)) +
  geom_bar(aes(y = after_stat(count/sum(count))))
```



```{r}
# covid_vac %>% 
# clean_names %>% 
# select(city_name, city_code, first_dose_80_89, second_dose_80_89) %>% 
#   filter(!(first_dose_80_89 == "<15")) %>% 
#   filter(!(second_dose_80_89 == "<15")) %>% 
#   group_by(city_code) %>% 
#   summarize(total_first_80s = count(first_dose_80_89), .groups = "drop")
```


```{r}
column_names <- covid_vac %>% 
  clean_names %>% 
  select(starts_with("first_dose"), starts_with("second_dose")) %>% 
  colnames() %>% 
  as.vector()


```

